Adaptive Video Streaming with Optimized Bitstream Extraction and PID-based Quality Control

### 2016-01-04 tmm.tex
Fix a typo found by a reviewer
Edit a little

In this section, we first introduce the \textit{quality level} concept to discretization the bitrate and quality of scalable video. Then we define the process variable used in our PID-based quality control algorithm. After that, the algorithm is formulated and explained in detail, followed by the brief discussion of parameter selection.

@@

\begin{table*}[t]
\centering
\caption{Luma PSNR gain of the proposed algorith compared with JSVM}
\label{tab:extraction-gain}
\begin{minipage}{0.95\linewidth}
% \renewcommand{\thefootnote}{\thempfootnote}
\centering
\begin{tabular}{c|c|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}| 
p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}}
%% |l|l| to left justify each column entry
%% |c|c| to center each column entry
%% use of \rule[]{}{} below opens up each row
\hline \hline
\multicolumn{2}{c|}{Sequence} &
{\em Bus} & {\em City} & {\em Crew} & {\em Football} & {\em Foreman} & {\em Harbour} & {\em Mobile} & {\em Soccer} \\ \hline 
\multirow{2}{*}{JSVM QL, $K$ = 32 \footnote{\label{footnote:JSVM_QL} Comparing the proposed algorithm with JSVM QL; the optimization window containing 32 frames}}
& Max\footnote{\label{footnote:max} Maximum PSNR gain through all bitrate constraints}
& 0.37 & 0.50 & 0.13 & 0.22 & 0.23 & 0.19 & 0.25 & 0.44 \\ \cline{2-10}
& Ave\footnote{\label{footnote:ave} Average PSNR gain through all bitrate constraints}
& 0.11 & 0.11 & 0.05 & 0.12 & 0.05 & 0.05 & 0.06 & 0.13 \\ \hline
\multirow{2}{*}{JSVM Basic, $K$ = 32}
& Max & 0.50 & 0.83 & 0.32 & 0.29 & 0.50 & 0.34 & 0.61 & 0.53 \\ \cline{2-10}
& Ave & 0.18 & 0.37 & 0.20 & 0.15 & 0.22 & 0.15 & 0.25 & 0.29 \\ \Xhline{2\arrayrulewidth}
\multirow{2}{*}{JSVM QL, $K$ = 48}
& Max & 0.36 & 0.39 & 0.27 & 0.30 & 0.30 & 0.38 & 0.21 & 0.40 \\ \cline{2-10}
& Ave & 0.12 & 0.23 & 0.16 & 0.13 & 0.15 & 0.13 & 0.08 & 0.21 \\ \hline
\multirow{2}{*}{JSVM Basic, $K$ = 48}
& Max & 0.36 & 0.81 & 0.32 & 0.29 & 0.49 & 0.47 & 0.57 & 0.60 \\ \cline{2-10}
& Ave & 0.19 & 0.40 & 0.19 & 0.17 & 0.28 & 0.22 & 0.28 & 0.42 \\ \hline
\end{tabular}
\end{minipage}
\end{table*}

>>>>

In this section, we first introduce the \textit{quality level} concept to discretize the bitrate and quality of scalable video. Then we define the process variable used in our PID-based quality control algorithm. After that, the algorithm is formulated and explained in detail, followed by the brief discussion of parameter selection.

@@

\begin{table*}[t]
\centering
\caption{Luma PSNR gain of the proposed algorithm compared with JSVM}
\label{tab:extraction-gain}
\begin{minipage}{0.95\linewidth}
% \renewcommand{\thefootnote}{\thempfootnote}
\centering
\begin{tabular}{c|c|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}| 
p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}}
%% |l|l| to left justify each column entry
%% |c|c| to center each column entry
%% use of \rule[]{}{} below opens up each row
\hline \hline
\multicolumn{2}{c|}{Sequence} &
{\em Bus} & {\em City} & {\em Crew} & {\em Football} & {\em Foreman} & {\em Harbour} & {\em Mobile} & {\em Soccer} \\ \hline 
\multirow{2}{*}{JSVM QL, $K$ = 32 \footnote{\label{footnote:JSVM_QL} Comparing the proposed algorithm with JSVM QL; the optimization window containing 32 frames}}
& Max\footnote{\label{footnote:max} Maximum PSNR gain through all bitrate constraints}
& 0.37 & 0.50 & 0.13 & 0.22 & 0.23 & 0.19 & 0.25 & 0.44 \\ \cline{2-10}
& Ave\footnote{\label{footnote:ave} Average PSNR gain through all bitrate constraints}
& 0.11 & 0.11 & 0.05 & 0.12 & 0.05 & 0.05 & 0.06 & 0.13 \\ \hline
\multirow{2}{*}{JSVM Basic, $K$ = 32}
& Max & 0.50 & 0.83 & 0.32 & 0.29 & 0.50 & 0.34 & 0.61 & 0.53 \\ \cline{2-10}
& Ave & 0.18 & 0.37 & 0.20 & 0.15 & 0.22 & 0.15 & 0.25 & 0.29 \\ \Xhline{2\arrayrulewidth}
\multirow{2}{*}{JSVM QL, $K$ = 48}
& Max & 0.36 & 0.39 & 0.27 & 0.30 & 0.30 & 0.38 & 0.21 & 0.40 \\ \cline{2-10}
& Ave & 0.12 & 0.23 & 0.16 & 0.13 & 0.15 & 0.13 & 0.08 & 0.21 \\ \hline
\multirow{2}{*}{JSVM Basic, $K$ = 48}
& Max & 0.36 & 0.81 & 0.32 & 0.29 & 0.49 & 0.47 & 0.57 & 0.60 \\ \cline{2-10}
& Ave & 0.19 & 0.40 & 0.19 & 0.17 & 0.28 & 0.22 & 0.28 & 0.42 \\ \hline
\end{tabular}
\end{minipage}
\end{table*}
